QPLIB: A Library of Quadratic Programming Instances

### 2017-02-01 format.tex
add note that for binary variables, a different default for variable bounds may apply

$l_{d}$ & default value (real) for entries in $l$            & \\
$n^{l_{d}}$ & number of non-default entries (integer) in $l$    &  \\

@@

in $l$, if $n^{l_{d}}> 0$, one pair per line        &  \\

@@

$u_{d}$ & default value (real) for entries in $u$            & \\
$n^{u_{d}}$ & number of non-default entries (integer) in $u$    &  \\

@@

in $u$, if $n^{u_{d}}> 0$, one pair per line        &  \\

@@

\item [{[2]}]
for problems of type \texttt{**N} or \texttt{**B}, these lines/sections
are omitted.
\item [{[3]}]
for problems of type \texttt{L**}, this section is omitted.
\item [{[4]}]
for problems of type \texttt{**N}, \texttt{**B} or \texttt{**L},
this section is omitted.
\item [{[5]}]
for problems of type \texttt{*C*}, \texttt{*B*} or \texttt{*I*},
this section is omitted. In case of \texttt{*I*}, binary variable need to be specified as general integer variables with bounds 0 and 1.
\end{description}

>>>>

$l_{d}$ & default value (real) for entries in $l$            & [6] \\
$n^{l_{d}}$ & number of non-default entries (integer) in $l$    & [6] \\

@@

in $l$, if $n^{l_{d}}> 0$, one pair per line        &  [6] \\

@@

$u_{d}$ & default value (real) for entries in $u$            & [6] \\
$n^{u_{d}}$ & number of non-default entries (integer) in $u$    &  [6] \\

@@

in $u$, if $n^{u_{d}}> 0$, one pair per line        & [6] \\

@@

\item [{[2]}]
For problems of type \texttt{**N} or \texttt{**B}, these lines/sections
are omitted.
\item [{[3]}]
For problems of type \texttt{L**}, this section is omitted.
\item [{[4]}]
For problems of type \texttt{**N}, \texttt{**B} or \texttt{**L},
this section is omitted.
\item [{[5]}]
For problems of type \texttt{*C*}, \texttt{*B*} or \texttt{*I*},
this section is omitted. In case of \texttt{*I*}, binary variable need to be specified as general integer variables with bounds 0 and 1.
\item [{[6]}]
For problems of type \texttt{*B*} and for variables that are specified explicitly as binary variables, the default values for lower and upper bounds of a binary variables are assumed to be 0 and 1, respectively, independent of the specification of $l_d$ and $u_d$.
%Note, that in case of \texttt{*I*}, binary variable need to be specified as general integer variables with bounds 0 and 1.
\end{description}
